New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations

### 2019-12-23 nontex/install/windows/fn_installations.Rmd
new gist for atom sync, latex installation

>>>>

# Install Latex

Use a combination of overleaf and local compile. The goal is to have the same installation set-up for windows as well as linux. And hopefully, locally compilable file also can be compiled on overleaf (only use packages also available on overleaf).

There are several pieces of things to install:

1. latex compiler: pdflatex, etc
2. tex distributions: MikTex, texlive
    + these folders, once various packages are installed, could be very large, many GB
3. latex packages from distributions
3. editor (gui): Atom, texStudio, etc

## Uninstall

- uninstall *MiKTeX*: delete from programs, then delete remaining folder in Program Files.
- uninstall *texlive*: go to *c:/texlive*, delete the folder

## Install

*Install on Windows*

- [Install Texstudio](https://www.texstudio.org/)
- [Install texlive](https://www.tug.org/texlive/acquire-netinstall.html)

*Install on Ubuntu*

install texlive and texstudio ubuntu/debian.

```{bash}
sudo apt-get update
sudo apt-get install texlive-full
sudo apt-get install texstudio
```

## Compile in Atom

Install the [latex](https://github.com/thomasjo/atom-latex) package on atom.

```{bash}
# set TeX path
# C:\texlive\2019\bin\win32
```
